%-------------------------
% Resume in Latex
% Author : Dipin Nair
% For more information, see https://github.com/dipinknair/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}

%----------FONT----------
\usepackage{fontspec}
\setmainfont{Helvetica}

%----------PAGE SETUP----------
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%----------MARGINS----------
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%----------SECTION FORMATTING----------
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%----------CUSTOM COMMANDS----------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.24in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%----------RESUME START----------
\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Dipin Kunhambu Nair} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +1 5136200022 ~ \href{mailto:dipinknair619@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{dipinknair619@gmail.com}} ~ 
    \href{https://dipinknair.github.io/}{\raisebox{-0.2\height}\faGlobe\ \underline{dipinknair.github.io}} ~
    \href{https://linkedin.com/in/dipinknair619/}{\raisebox{-0.2\height}\faLinkedin\ \underline{LinkedIn}} ~
    \href{https://github.com/dipinknair}{\raisebox{-0.2\height}\faGithub\ \underline{GitHub}} ~
    Austin, TX
    \vspace{-8pt}
\end{center}

%----------SUMMARY----------
\section{Summary}
{Software engineer with 7+ years of experience building production-level Python and C++ software for simulation, automation, and developer tooling. Maintains PyMechanical and contributes to the PyAnsys open-source ecosystem, with ownership of testing, releases, CI/CD, and documentation. Seeking software roles focused on scalable Python platforms, open-source tooling, and reliable customer-facing software.}
\vspace{-8pt}

%----------EDUCATION----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Cincinnati}{January 2021 -- August 2023}
      {Master of Science in Mechanical Engineering | GPA: 4.0/4.0}{Cincinnati, Ohio}
    \resumeSubheading
      {Indian Institute of Technology, Hyderabad}{August 2012 -- August 2016}
      {Bachelor of Technology in Mechanical Engineering | GPA: 8.24/10}{Hyderabad, India}
  \resumeSubHeadingListEnd
\vspace{-8pt}

%----------SKILLS----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming}{: Python, C++, C\#, MATLAB} \\
     \textbf{Software Engineering}{: Unit Testing, Integration Testing, Regression Testing, Object-Oriented Programming, Agile/Scrum} \\
     \textbf{Tools/DevOps}{: Git, Docker, Linux, GitHub Actions, Azure DevOps, CI/CD} \\
    }}
 \end{itemize}
 \vspace{-16pt}

%----------PROFESSIONAL EXPERIENCE----------
\section{Professional Experience}

  \resumeSubHeadingListStart
  \vspace{1pt}
    \resumeSubheading
      {Synopsys Inc.}{May 2023 -- Present}
      {Senior Software Engineer}{Austin, Texas}
      \resumeItemListStart
        \resumeItem{Architected and maintained PyMechanical, a PyAnsys open-source Python library enabling programmatic access to Ansys Mechanical.}
        \resumeItem{Engineered Docker-based containerization and Azure DevOps CI/CD pipelines, reducing release cycles by 30\% across Windows and Linux platforms.}
        \resumeItem{Developed unit and integration testing frameworks, increasing automated regression coverage from 70\% to 90\%.}
        \resumeItem{Resolved critical production bugs in ANSYS Mechanical core software (C++/C\#) and improved reliability of customer-facing workflows.}
      \resumeItemListEnd

    \resumeSubheading
      {Ansys Inc.}{January 2023 -- April 2023}
      {Software Developer Intern}{Pittsburgh, Pennsylvania}
      \resumeItemListStart
        \resumeItem{Contributed ANSYS Mechanical release features with the Linear Dynamics team, supporting production C++/C\# development workflows.}
        \resumeItem{Validated changes through Windows/Linux developer builds, Azure pipelines, and ARM tests before integration.}
        \resumeItem{Applied COM principles to extend Mechanical interfaces; partnered with test teams to triage defects and document release functionality.}
      \resumeItemListEnd

    \resumeSubheading
      {Procter \& Gamble}{August 2021 -- August 2022}
      {Robotics Research Assistant}{Cincinnati, Ohio}
      \resumeItemListStart
        \resumeItem{Automated fragrance consumption analysis for 600+ air fresheners using robotic batch testing workflows.}
        \resumeItem{Enabled robot weighing, QR-code computer vision, and validated data uploads to Siemens server workflows.}
        \resumeItem{Created a Python PyQt GUI to improve customer interaction and standardize test execution.}
      \resumeItemListEnd

    \resumeSubheading
      {Tata Consultancy Ltd}{October 2019 -- December 2020}
      {Systems Engineer}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Earned Design for Six Sigma Black Belt certification by supervising 2 projects as team leader and facilitator.}
        \resumeItem{Coordinated development of 12 efficiency modules in MASTA software using C++.}
        \resumeItem{Led a cross-functional team of 4 to automate meshing in SimLab using JavaScript for simulation analysis.}
      \resumeItemListEnd

    \resumeSubheading
      {General Motors}{September 2016 -- September 2019}
      {Senior Engineer}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Automated Abaqus system modeling with VBA scripting, reducing manual effort by 85\%.}
        \resumeItem{Earned 7 recognitions, including Work of Wonder and Pat on the Back, for transmission efficiency optimization.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd
\vspace{-14pt}

\end{document}